\textls[-0]{\thetitle}

### 2023-03-22 canonicitymodel.tex
resolve comment

    \begin{cases}
      \{\star^1\} & \text{if } t \equiv \true \\
      \{\star^2\} & \text{if } t \equiv \false
    \end{cases}\YZ{Is this more accurate than 'disjoint union'?}\EDJreply{It is accurate. It is actually the way Coquand write it. But I find this way weird type-theoretically---at the very end, when we want to prove a closed term t is either true or false, we will use this cB. But defining in this Coquand way, type-theoretically, we cannot extract a proof term t = true. (i.e. there is no proof term stored here!). I know my above sentence is a bit awkward but I just find this Coquand way of saying very...counter-intuitive.}
%   \setc{\star^1}{ \text{ when } t \equiv \true } \dot{\cup} \setc{\star^2}{\text{ when } t \equiv \false } \quad \text{disjoint union} \\

@@

The eccentric part of the proof-relevant logical-relations model is the
treatment of propositions.
The model treats proposition in a special way : \EDJ{Without this first sentence, this paragraph seems unmotivated.}\YZreply{Why is it 'difficult'? Is there a more appropriate adjective than 'difficult'?}\EDJreply{Don't you find difficult? At first sight, I cannot understand why this sentence, proposed by Sterling in two of his paper, can be valid mathematically. It only makes sense to me until I am in a type-theoretic world (by Kaposi, since Eq is an inductive type now) (or maybe topos-theoretically where categorical logic will encode equality using data like equalizer). What about changing the phrase to "eccentric" or "weird"?}
a proposition is encoded as a sub\-singleton. For
example, $\{\star^1 \ | \text{ when } t \equiv \true  \} \dot{\cup} \{\star^2 \
| \text{ when } t \equiv \false  \}$ represents a disjoint union of two
sub\-singleton sets, where the first one is either a singleton if we have a proof of
$t \equiv \true $ or an empty set otherwise.
In other words,
$\star^1$ witnesses a proof that $t \equiv \true$.
Here, $\star$, $\star^1$, $\star^2$ are just some arbitrary fixed elements.

>>>>

    %\YZ{Is this more accurate than 'disjoint union'?}\EDJreply{It is accurate. It is actually the way Coquand write it. But I find this way weird type-theoretically---at the very end, when we want to prove a closed term t is either true or false, we will use this cB. But defining in this Coquand way, type-theoretically, we cannot extract a proof term t = true. (i.e. there is no proof term stored here!). I know my above sentence is a bit awkward but I just find this Coquand way of saying very...counter-intuitive.}
  \setc{\star^1}{ \text{ when } t \equiv \true } \uplus \setc{\star^2}{\text{ when } t \equiv \false } \quad \text{disjoint union} \\

@@

The eccentric part of the proof-relevant logical-relations model is the
treatment of propositions.
The model treats proposition in a special way : \EDJ{Without this first sentence, this paragraph seems unmotivated.}\YZreply{Why is it 'difficult'? Is there a more appropriate adjective than 'difficult'?}\EDJreply{Don't you find difficult? At first sight, I cannot understand why this sentence, proposed by Sterling in two of his paper, can be valid mathematically. It only makes sense to me until I am in a type-theoretic world (by Kaposi, since Eq is an inductive type now) (or maybe topos-theoretically where categorical logic will encode equality using data like equalizer). What about changing the phrase to "eccentric" or "weird"?}
a proposition is encoded as a sub\-singleton. For
example, $\{\star^1 \ | \text{ when } t \equiv \true  \} \uplus \{\star^2 \
| \text{ when } t \equiv \false  \}$ represents a disjoint union of two
sub\-singleton sets, where the first one is either a singleton if we have a proof of
$t \equiv \true $ or an empty set otherwise.
In other words,
$\star^1$ witnesses a proof that $t \equiv \true$.
Here, $\star$, $\star^1$, $\star^2$ are just some arbitrary fixed elements.
